The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
remove "see the next point", because the next point is unrelated.  If there is something else supporting the experimental transformation of velocity data, it would be helpful to reference its section directly

\subsubsection{Proper motion and velocity transformations}
    In addition to positional coordinate data, the \texttt{Frame} classes now
    also support velocity data.
    As the default representation for most frames is spherical, most of the
    \texttt{Frame} classes expect proper motion and radial velocity components
    to specify the velocity information.
    The names of the proper motion components all start with \texttt{pm} and
    adopt the same longitude and latitude names as the positional components.
    Transforming coordinates with velocity data is also supported, but in some
    cases the transformed velocity components have limited accuracy because the
    transformations are done numerically instead of analytically.
    The low-level interface for specifying and transforming velocity data (see
    the next point) is currently experimental.
    As such, in version 2.0, only the \texttt{Frame} classes (and not the
    \texttt{SkyCoord} class) support handling velocities.

>>>>

\subsubsection{Proper motion and velocity transformations}
    In addition to positional coordinate data, the \texttt{Frame} classes now
    also support velocity data.
    As the default representation for most frames is spherical, most of the
    \texttt{Frame} classes expect proper motion and radial velocity components
    to specify the velocity information.
    The names of the proper motion components all start with \texttt{pm} and
    adopt the same longitude and latitude names as the positional components.
    Transforming coordinates with velocity data is also supported, but in some
    cases the transformed velocity components have limited accuracy because the
    transformations are done numerically instead of analytically.
    The low-level interface for specifying and transforming velocity data  is
    currently experimental.  As such, in version 2.0, only the \texttt{Frame}
    classes (and not the \texttt{SkyCoord} class) support handling velocities.
